%====================
% EXPERIENCE A
%====================
\subsection{Data Nest \hfill 11/2025 -- Present}
\subtext{Data Scientist}
\begin{zitemize}
    \item \textbf{Lead generation and lookalike model}: Analyzed complex business processes to define strategic Proxy Labels. Design evaluation metric of lookalike model to ensure lead quality. Build end-to-end training pipeline of lookalike model.  
    \item \textbf{Location Feature Engineering}: Designed and built an end-to-end spatio-temporal feature system converting raw telecom logs (Voice, SMS, HLR/VLR) from VNPT \& Viettel into subscriber behavioral features for credit scoring. Replaced static cell mapping with a 6-month dynamic join window, resolved Vietnam's administrative boundary restructuring, and deployed automated null-rate \& cell-count drift monitoring. Feature architecture: 3-layer granularity (Cell/District/Province), 4 behavioral profiles (Home/Work/Weekend/All), spatial metrics including Radius of Gyration, Spatial Entropy, Earth Mover's Distance, and Meta RWI enrichment via spatial join. Improved Gini across 5 of 6 credit scoring models on VNPT data, peak gain \textbf{+3.12\% Gini}.
    \item \textbf{HDBank BNPL Model Enhancement}: Identified and fixed a data leakage in the legacy evaluation framework by enforcing temporal train/test split. Discovered the Inter-Arrival-Time (IAT) feature during Service Number Detection R\&D --- a behavioral signal capturing call-interval patterns. Used \textbf{PySpark ML} to evaluate a 200+ feature inventory and select the top 50 by importance. Integrated HDBank credit card data into BNPL training set to capture bank-specific default behavior. Final model achieved \textbf{+1.76 Gini} uplift on BNPL portfolio and \textbf{+2.17 Gini} on CC portfolio, narrowing the gap with the legacy CC-specialist model to under 2 points.
\end{zitemize}
\subsection{Deliveree on-demand logistics \hfill 10/2024 -- 11/2025}
\subtext{Data Scientist}
\begin{zitemize}
    \item \textbf{Dynamic Pricing (built from scratch)}: Achieved highest increment of GTV recorded is 40\% in A/B testing
    \begin{itemize}
        \item \textbf{Price–demand model (causal)}: From zero to production — set the goal, collected/cleaned event data, built a model to measure how price changes affect demand, ran experiments, and deployed with \textbf{Ray Job}. Added shadow rollout and monitoring.

        \item \textbf{Potential demand model}: Changed the forecast target from 1 hour to 3 hours (with upsampling) after checking the uncertainty in estimates. This made pricing more statistically reasonable. 
        \item Supply model: Designed a new supply model to replace the old “not-fulfilled” model. Prove by causal inference that the effect of price is not significant on new target in case of our business. Relax the assumption about causality of supply.  
        \item \textbf{Price safety}: Proposed and tested a statistical guardrail to catch market reactions and adjust prices if needed, so prices don’t swing too far in case the pricing system go wrong.
        \item \textbf{Engineering}: Built the pricing API with \textbf{Ray Serve}, trained models on \textbf{Google Vertex AI Pipelines}, and set up \textbf{Grafana} dashboards for monitoring, design model output pipeline on Postgresql to ensure the availability of data.
        \end{itemize}
\end{zitemize}
\begin{zitemize}
\item \textbf{Driver matching system (enhancement)}: \begin{itemize}
        \item Define and collect data from the driver portfolio.
        \item Build error analysis tree: point out the cohort that have low accuracy
        \item Optimize training flow: re-write sampling method for lower the training time from 12 hour to under 2 hour. 
    \end{itemize}

\end{zitemize}
\subsection{Thesis : Speech Enhancement using deep-learning on edge device \hfill 01/2023 -- 06/2023}
\begin{zitemize}
\item Applied DCCRN model with feature fusion and similarity-preserved knowledge distillation to compress a speech enhancement model for edge deployment. Implemented complex-number neural networks in PyTorch and optimized multi-GPU training with PyTorch Lightning. \textbf{Grade: 9.1/10} \href{https://drive.google.com/file/d/1KO6Zd68ePfUTPycaNw94ThQVt2Pkan7s/view?usp=sharing}{[thesis]}
\end{zitemize}
\subsection{{Timo Digital Bank \hfill 04/2023 -- 06/2024}}
\subtext{Data Scientist}
\begin{zitemize}
\item Developed an expense prediction model by redefining the target variable and implementing a data pipeline with \textbf{dbt} and \textbf{Airflow}. Delivered insights through dashboards on \textbf{Holistics} and personalized customer engagement using \textbf{Mandrill}.
\item Enhanced transaction purpose classification by applying \textbf{rule mining}, \textbf{Elasticsearch} (TF-IDF, Bayesian clustering), and advanced evaluation with \textbf{EvidentlyAI}. Deployed the improved model as an API service using \textbf{SpringData}.
\item Designed and implemented graph algorithms (\textbf{DFS, BFS, heuristic growth}) on 4TB of user interaction data with \textbf{PySpark}, uncovering customer behavior patterns that informed UI/UX improvements in money transfer and adding contact flows.

\item \href{https://www.linkedin.com/in/annabelleleanh/}{Referral : Ngoc Anh - Head of Data at Timo}
\end{zitemize}

\subsection{{Vietnam International Bank(VIB) Customer Data Platform\hfill 09/2022 -- 01/2023}}
\subtext{Vendor Data Scientist \hfill Bluebolt software}
\begin{zitemize}
\item Scoped DS use cases (churn prediction, spending regression, recommendation) by auditing data across VIB's card, digital, and marketing departments. Assessed data quality and built dashboards on SAP to track DS metrics for the BA team.
\end{zitemize}






%====================
% EXPERIENCE B
%====================
%
% \subsection{{University Entrance Score Data visualize with Tableau \hfill 05/2022}}
% \subtext{school project, Team size : 5 \hfill HCMUS}
% \begin{zitemize}
% \item \textbf{Languague-tool} : Python, html-request, Tableau
% \item Data crawling : crawl from various websites using Python script (html-request, regex, pandas data-frame)
% \item Data processing with pandas(Python) : Analyse (base on experience,research) to find and remove redundancy row , merge files from many years, region to single Data-frame using built-in method in Pandas library and import to Tableau. 
% \item Visualize data using Tableau : make graph and build interactive dashboard. 
% \item Extract insight about score by region, trend entrance score, anomaly detection (fraud detection) from dashboard, graph and information research, inference on internet. 
% \item Merge other member's to one tableau file and deploying project on Tableau public website. 
% \item \href{https://public.tableau.com/views/DV-final/TngquanimchuncctrngH}{Reference}
% \end{zitemize}
%
%====================
% EXPERIENCE C
%====================

%====================
% EXPERIENCE D
%====================


%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
